---
title: "elements"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Elements of Customized RMarkdown Templates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(indiedown)
```

Indiedown packages use R functions to generate LaTeX code for customization.

### Writing your own LaTeX generator functions.

For most customizations, it is recommended to turn off the default LaTeX title page, and create your own title page via LaTeX commands. The basic repertory are the LaTeX commands `\large`, `\Large`, `\LARGE`, `\huge`, etc., along witch `vspace{1ex}`, but all LaTeX trickery can be applied. The LaTeX helper functions should be put to the `R` folder of your package.


### Usage demonstration by templates

RMarkdown Templates demonstrate the use of a customized style. RMarkdown requires you to put them to `inst/rmarkdown/templates/mytemplate`.
RStudio will recognize them and show them when you click 'New RMarkdown Document' and 'from Template'.
You can also use `usethis::use_rmarkdown_template()` to add a new template.


